---
output: html_document
---


```{r setup, echo=FALSE, message=FALSE, warning = FALSE}

library(tidyverse)
library(lubridate)
library(ggmap)
library(scales)

knitr::opts_chunk$set(fig.width = 12, fig.height = 10)
readr.show_progress=FALSE

twitter <- read_delim(
                    "E:\\uni\\Cluster and Cloud Computing\\COMP90024-Project\\assignment2\\TwitterExplorer\\Analysis\\GenerateStats\\bin\\volumeStats.csv",
                    ",", col_types = "cDlli", quote = '', progress = FALSE)

tdata <- filter(twitter, YearMth >= ymd(20170701), YearMth <= ymd(20180331))

locations <- read_delim(
                    "E:\\uni\\Cluster and Cloud Computing\\COMP90024-Project\\assignment2\\TwitterExplorer\\Analysis\\GenerateStats\\bin\\locations.csv",
                    ",", col_types = "cDlli", quote = '', progress = FALSE)

uu <- read_delim(
                    "E:\\uni\\Cluster and Cloud Computing\\COMP90024-Project\\assignment2\\TwitterExplorer\\Analysis\\GenerateStats\\bin\\geoUsersPerMth.csv",
                    ",", col_types = "Di", quote = '', progress = FALSE)
users <- filter(uu, YearMth >= ymd(20170701), YearMth <= ymd(20180331))


timeOfDay <- read_delim(
                    "E:\\uni\\Cluster and Cloud Computing\\COMP90024-Project\\assignment2\\TwitterExplorer\\Analysis\\GenerateStats\\bin\\timeOfDayActivity.csv",
                    ",", quote = '', progress = FALSE)


totalNumberTweets <- tdata %>% select(Count) %>% sum()
totalGeoTweets <- filter(tdata, HasGeo) %>% select(Count) %>% sum()

```


## Summary of Calibration Data

A set of historical tweets, already captured by the University, were used to calibrate additional analysis and data visualisation.  

The calibration set consisted of:

* `r comma(totalNumberTweets) `   distinct Geo-located tweets  
* covering the following Australian capital cities:
    + Adelaide
    + Brisbane
    + Canberra
    + Hobart
    + Melbourne
    + Perth
    + Sydney

* for the period 1st July, 2017 to 31 March, 2018

*  `r percent(totalGeoTweets/totalNumberTweets) ` of the tweets where posted with GPS coordinates (Exact Location Tweets)

* covering `r comma(nrow(locations) %>% sum()) ` distinct locations


### Explorative Statistics 


```{r echo=FALSE,warning = FALSE, fig.height = 6}
allCityTtls <- tdata %>%
     group_by(YearMth) %>%
     summarise(Tally = sum(Count)) %>%
     mutate(Location = "Total") %>%
     select(Location,YearMth,Tally)

byCityTtls <- tdata %>%
     group_by(Location, YearMth) %>%
     summarise(Tally = sum(Count)) %>%
      ungroup()

# byCityTtls<-bind_rows(byCityTtls, allCityTtls)   

ggplot(data = byCityTtls, aes(x = YearMth, y = Tally, group = Location, colour = Location)) +     
     geom_line() +
     geom_point() +
     geom_line(data = allCityTtls, aes(x = YearMth, y = Tally, group = Location, colour = Location), size = 1, linetype = "longdash") +
     xlab('Month Year') +
     ylab('Tweet Tally') +
     scale_color_brewer(palette = 'Dark2') +
     scale_y_continuous(labels = comma) +
     scale_x_date(date_breaks = "1 month", date_labels = "%b %y") +
     labs(title="Volume of geo-located tweets by month")

```




```{r echo=FALSE,warning = FALSE,, fig.height = 6}
allCityTtls <- filter(tdata, HasGeo) %>%
     group_by(YearMth) %>%
     summarise(Tally = sum(Count)) %>%
     mutate(Location = "Total") %>%
     select(Location,YearMth,Tally)

byCityTtls <- filter(tdata, HasGeo) %>%
     group_by(Location, YearMth) %>%
     summarise(Tally = sum(Count)) %>%
      ungroup()

# byCityTtls<-bind_rows(byCityTtls, allCityTtls)   

ggplot(data = byCityTtls, aes(x = YearMth, y = Tally, group = Location, colour = Location)) +
     geom_line() +
     geom_point() +
     geom_line(data = allCityTtls, aes(x = YearMth, y = Tally, group = Location, colour = Location), size = 1, linetype = "longdash") +
     scale_color_brewer(palette = 'Dark2') +
     xlab('Month Year') +
     ylab('Tweet Tally') +
     scale_y_continuous(labels = comma) +
     scale_x_date(date_breaks = "1 month", date_labels = "%b %y") +
     labs(title="Volume of tweets with exact locations (GPS coordinates) by month")

```




```{r echo=FALSE,warning = FALSE,, fig.height = 6}

ggplot(data = users, aes(x = YearMth, y = DistinctUsers)) +
     geom_line(color='red', size=1) +
     xlab('Month Year') +
     ylab('Distinct Users') +
     scale_y_continuous(labels = comma) +
     scale_x_date(date_breaks = "1 month", date_labels = "%b %y") +
     labs(title="Number of distinct users who have posted geo-gocated tweets in given month")

```



```{r echo=FALSE,warning = FALSE,, fig.height = 6}

group_by(timeOfDay, Hour) %>%
    summarise(Tally = sum(Count)) %>%
    ggplot(aes(x = Hour, y = Tally)) +
    geom_col(fill='red4') +
     xlab('Hour of Day (LocalTime)') +
     ylab('Total volume of Tweets in hour [h,h+1) of day') +
     scale_y_continuous(labels = comma) +    
     labs(title="Variation in geo-located tweets volumes with time of day")

```



```{r echo=FALSE,warning = FALSE,, fig.height = 6}


dw <- group_by(timeOfDay, DayOfWeek) %>%
    summarise(Tally = sum(Count))
dw$DayOfWeek <- as.factor(dw$DayOfWeek)
dw$DayOfWeek <- factor(dw$DayOfWeek, levels(dw$DayOfWeek)[c(4, 2, 6, 7, 5, 1, 3)])


ggplot(data = dw, aes(x = DayOfWeek, y = Tally)) +
     geom_col(fill='red4') +
     xlab('Day of Week (LocalTime)') +
     ylab('Total Volume of Tweets in day of week') +
     scale_y_continuous(labels = comma) +    
     labs(title="Variation in geo-located tweets volumes with day of week")

```