---
output: html_document
---


```{r setup, echo=FALSE, message=FALSE, warning = FALSE}

library(tidyverse)
library(lubridate)
library(ggmap)
library(scales)

knitr::opts_chunk$set(fig.width = 12, fig.height = 10)
readr.show_progress=FALSE

insta <- read_delim("E:\\uni\\Cluster and Cloud Computing\\assign2\\TwitterExplore\\TwitterExplore\\bin\\location-2018.csv", ",", col_types = "nnn", quote = '', progress = FALSE)



```

## Tweeter Mobility

It was observed that tweets originated by a proportion of posters from multiple cities.
Assuming that the city with the most tweets, was the posters home city some insight to the posters mobility and behaviour can be
obtained by analysing the use 

### Assumptions

The analysis is based on the following assumptions:

* the city with the most tweets for a given poster, is the home city of the poster
* users that poster from multiple geographic locations are likely to be actual end-users not businesses (e.g. bars, venues, etc.).
There are some small number of services (e.g. _Where Pets Are Found, CEB Jobs_ ) that post from multiple cities.
These anomalies have not been filtered.







```{r echo=FALSE,warning = FALSE, fig.height = 6}

ggmap(get_stamenmap(region, maptype = "toner-lite")) +
    geom_point(data = pts, aes(x = Xloc, y = Yloc, size = Freq, alpha = Freq), color = 'navy') +
    scale_alpha(trans = 'log10') +
    xlab('Longitude') +
    ylab('Latitude') +
    theme(legend.position = "none") +
lab(title="")

```



