---
output: html_document
---


```{r setup, echo=FALSE, message=FALSE, warning = FALSE}

library(tidyverse)
library(lubridate)
library(ggmap)
library(scales)

knitr::opts_chunk$set(fig.width = 12, fig.height = 10)
readr.show_progress=FALSE

toJourneysUsers <- read_csv(
                    "E:\\uni\\Cluster and Cloud Computing\\COMP90024-Project\\assignment2\\TwitterExplorer\\Analysis\\GenerateStats\\bin\\geoJourneysUsers.csv",
                   progress = FALSE)
toJourneysTweets <- read_csv(
                    "E:\\uni\\Cluster and Cloud Computing\\COMP90024-Project\\assignment2\\TwitterExplorer\\Analysis\\GenerateStats\\bin\\geoJourneysActivity.csv",
                   progress = FALSE)

toJourneysAvg <- inner_join(toJourneysUsers, toJourneysTweets, by = c("Source", "X1", "Y1", "X2", "Y2", "Target"))


geoTo <- read_csv("E:\\uni\\Cluster and Cloud Computing\\COMP90024-Project\\assignment2\\TwitterExplorer\\Analysis\\GenerateStats\\bin\\geoToJourneys.csv",
                   progress = FALSE)

region<- c(left=111, right=157, bottom=-46,top=-23)

```

## Tweeter Mobility

It was observed that tweets originated by a proportion of posters from multiple cities.
Assuming that the city with the most tweets, was the posters home city some insight to the posters mobility and behaviour can be
obtained by analysing the use 

### Assumptions

The analysis is based on the following assumptions:

* the city with the most tweets for a given poster, is the home city of the poster
* users that poster from multiple geographic locations are likely to be actual end-users not businesses (e.g. bars, venues, etc.).
There are some small number of services (e.g. _Where Pets Are Found, CEB Jobs_ ) that post from multiple cities.
These anomalies have not been removed in this analysis.




### Number of mobile tweeters

Based on geo-located (place tagged and exact-position) data for `r comma(sum(toJourneysUsers$Users))` individual posters


```{r echo=FALSE,warning = FALSE, fig.height= 6}

srcCity <- filter(toJourneysUsers, Source == "melbourne")

ggmap(get_stamenmap(region, zoom = 4, maptype = "toner-lite")) +
    geom_segment(data = srcCity,
        aes(x = X1, y = Y1, xend = X2, yend = Y2, size = Users),
        arrow = arrow(angle = 20), lineend = 'square', color = 'deeppink4', alpha = 0.5) +
        geom_point(data = srcCity, aes(x = X1, y = Y1),
        size = 4, color = 'deeppink4') +
        xlab('') +
        ylab('') +
        labs(title = 'Number of Melbourne residents who have tweeted in other cities') +
        labs(caption = 'Line width is proportional to number of tweeters who visit linked city') 
      

```



```{r echo=FALSE,warning = FALSE, fig.height= 6}

srcCity <- filter(toJourneysUsers, Target == "melbourne")

ggmap(get_stamenmap(region, zoom = 4, maptype = "toner-lite")) +
    geom_segment(data = srcCity,
        aes(x = X1, y = Y1, xend = X2, yend = Y2, size = Users),
        arrow = arrow(angle = 13), lineend = 'square', color = 'green4', alpha = 0.5) +
    geom_point(data = srcCity, aes(x = X1, y = Y1),
        size = 4, color = 'green4') +
        xlab('') +
        ylab('') +
        labs(title = 'Number of non-Melbourne residents who tweeted when visiting Melbourne') +
         labs(caption = 'Line width is proportional to number of tweeters who visit linked city') 
         

```


### Tweeting activity of mobile tweeters

Based on `r comma(sum(toJourneysTweets$Tweets))` geo-located (place tagged and exact-position) tweets by `r comma(sum(toJourneysUsers$Users))` individual posters


```{r echo=FALSE,warning = FALSE, fig.height= 6}

srcCity <- filter(toJourneysAvg, Source == "melbourne")

ggmap(get_stamenmap(region, zoom = 4, maptype = "toner-lite")) +
    geom_segment(data = srcCity,
        aes(x = X1, y = Y1, xend = X2, yend = Y2, size = Tweets/Users),
        arrow = arrow(angle = 20), lineend = 'square', color = 'deeppink4', alpha = 0.5) +
        geom_point(data = srcCity, aes(x = X1, y = Y1),
        size = 4, color = 'deeppink4') +
        xlab('') +
        ylab('') +
        labs(title = 'Mean tweets by Melbourne residents who tweeted while in other cities') +
         labs(caption = 'Line width is proportional to average tweets') 
        
```



```{r echo=FALSE,warning = FALSE, fig.height= 6}

srcCity <- filter(toJourneysAvg, Target == "melbourne")

ggmap(get_stamenmap(region, zoom = 4, maptype = "toner-lite")) +
    geom_segment(data = srcCity,
        aes(x = X1, y = Y1, xend = X2, yend = Y2, size = Tweets/Users),
        arrow = arrow(angle = 13), lineend = 'square', color = 'green4', alpha=0.5) +
    geom_point(data = srcCity, aes(x = X1, y = Y1),
        size = 4, color = 'green4') +
        xlab('') +
        ylab('') +
        labs(title = 'Mean tweets by non-Melbourne residents who tweeted when visiting Melbourne') +
         labs(caption = 'Line width is proportional to average tweets') 
           

```



### Tweeted from distinations of mobile tweeters

Based on `r  comma(nrow(geoTo))` geo-located  exact-position  by `r comma(sum(toJourneysUsers$Users))` individual posters,


```{r echo=FALSE,warning = FALSE, fig.height= 7}

region <- c(left = 144.91, right = 145.0, top = -37.78, bottom = -37.875)
innermelb <- filter(geoTo,
                    region['left'] <= X2 & X2 <= region['right'],
                    region['top'] >= Y2 & Y2 >= region['bottom'])

ggmap(get_stamenmap(region, zoom = 14, maptype = "toner-lite")) +
    stat_density_2d(data = innermelb, aes(x = X2, y = Y2, fill = ..level..), geom = "polygon", alpha = 0.5) +
    scale_fill_distiller(palette = "Spectral") +
    geom_point(data = innermelb, aes(x = X2, y = Y2), color = 'navy') +
    scale_alpha(trans = 'log10') + xlab('Longitude') + ylab('Latitude') +
    theme(legend.position = "none") +
    labs(title = 'Locations tweeted from by non-Melbourne residents who tweeted when visiting inner-Melbourne') 
        
```


```{r echo=FALSE,warning = FALSE, fig.height= 7}

region <- c(left = 151.185, right = 151.23, top = -33.842, bottom = -33.875)
innersyd <- filter(geoTo,
                    region['left'] <= X2 & X2 <= region['right'],
                    region['top'] >= Y2 & Y2 >= region['bottom'])

ggmap(get_stamenmap(region, zoom = 15, maptype = "toner-lite")) +
    stat_density_2d(data = innersyd, aes(x = X2, y = Y2, fill = ..level..), geom = "polygon", alpha = 0.5) +
    scale_fill_distiller(palette = "Spectral") +
    geom_point(data = innersyd, aes(x = X2, y = Y2), color = 'navy') +
    scale_alpha(trans = 'log10') + xlab('Longitude') + ylab('Latitude') +
    theme(legend.position = "none") +
    labs(title = 'Locations tweeted from by non-Sydney residents who tweeted when visiting inner-Sydney') 
        
```